---
title: "analysis"
author: "Jianan"
date: "2023-09-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(readxl)
library(tibble)
library(purrr)
library(plyr)
```

load the 100 simulations
```{r}
load("ventilator_carlifornia2.RData")
load("date.RData")
load("dataset.RData")
```


last_date of the crisis period
```{r}
table(last_date)
```

total number of patients after allocation for each day

```{r}
options(digits = 3)
sum_v <- rep(0, length(v_all[[1]]))
for(i in 1:length(v_all)){
  sum_v <- sum_v + v_all[[i]]
}
n2 <- sum_v/length(v_all)
np <- c(df3$number[1:90],n2)
names(np) <- d 
np
```

```{r}
options(digits = 3)
v_all_sd <- sapply(1:length(v_all[[1]]), function(j){sd(v_all %>% map_dbl(c(j)))})
v_all_sd <- c(rep(0,90),v_all_sd)
names(v_all_sd) <-d 
v_all_sd
```

survival rate for the cohort

```{r}
tl <- length(unique(allo2[allo2$date >= "2020-03-31" & allo2$date <= "2020-04-14",]$pat_enc_csn_id))
options(digits = 3)
survival <- 0
cohort_new[is.na(cohort_new$dead),]$dead <- 0
for (i in 1:length(allo3_all)) {
  df <- allo3_all[[i]][allo3_all[[i]]$date >= "2020-03-31" & allo3_all[[i]]$date <= "2020-04-14",]
  id <- unique(df$pat_enc_csn_id)
  survival <- table(cohort_new[cohort_new$pat_enc_csn_id %in% id,]$dead)[1]/tl + survival
}
survival/length(allo3_all)
```

(7) survival rate for group——give 

```{r}
a <- 0
for (i in 1:length(group_give_all)) {
  id <- group_give_all[[i]]$pat_enc_csn_id
  a <- table(cohort_new[cohort_new$pat_enc_csn_id %in% id,]$dead)[1]/length(id) + a
}
format(a/length(group_give_all),digits = 5)
```

(8) survival rate for group--receive

```{r}
cohort_new[is.na(cohort_new$dead),]$dead <- 0
b <- 0
for (i in 1:length(group_receive_all)) {
  id <- group_receive_all[[i]]$pat_enc_csn_id
  b <- table(cohort_new[cohort_new$pat_enc_csn_id %in% id,]$dead)[1]/length(id) + b
}
format(b/length(group_receive_all),digits = 5)
```

### 2. Race

```{r include = FALSE}
#race regroup
cohort_new <- add_column(cohort_new, race_new = NA)
cohort_new[cohort_new$race %in% c("White","Unknown, White",
                                  "Other Race, White","White, Other Race",
                                  "White, Unknown",
                                  "White, Other Pacific Islander",
                                  "White;Other Race",
                                  "White;Other Race",
                                  "Patient Refused;White",
                                  "Other Race;White"),]$race_new <- "White"
cohort_new[cohort_new$race %in% c("African American (Black)",
                                  "African American (Black), White",
                                  "African American (Black), Bangladeshi",
                                  "Chinese;African American (Black)",
                                  "White;African American (Black)",
                                  "Bangladeshi;African American (Black)"),]$race_new <- "African American"
cohort_new[cohort_new$race %in% c("Asian","Chinese","Chinese, Asian - unspecified","Japanese",
                                  "Pakistani","Bangladeshi","Asian - unspecified, Other Race",
                                  "Korean, Unknown","Other Pacific Islander","Asian Indian",
                                  "Asian - unspecified","Unknown, Chinese","Chinese, Other Race",
                                  "Filipino","Filipino, Other Pacific Islander",
                                  "Other Race, Chinese",
                                  "Asian;Asian - unspecified",
                                  "Korean","Other Race;Chinese",
                                  "Chinese;Asian - unspecified",
                                  "Vietnamese","Asian Indian;Other Race",
                                  "Asian - unspecified;Chinese",
                                  "Chinese;Asian"),]$race_new <- "Asian"
cohort_new[cohort_new$race %in% c("Native American (American Indian/Eskimo/Aleutian)",
                                  "Native American (American Indian/Eskimo/Aleutian) , Other Pacific Islander",
                                  "White;Native American (American Indian/Eskimo/Aleutian)",
                                  "Other Pacific Islander;Native American (American Indian/Eskimo/Aleutian)",
                                  "Native American (American Indian/Eskimo/Aleutian) ;African American (Black)",
                                  "Other Pacific Islander;White",
                                  "Filipino;Other Pacific Islander",
                                  "Native American (American Indian/Eskimo/Aleutian) ;African American (Black)"),]$race_new <- "Native American"
cohort_new[cohort_new$race %in% c("Unknown","Other Race",NA,"Patient Refused",
                                  "Unknown, Other Race","Other Race, Unknown","0"),]$race_new <- "Unknown"
cohort_new[is.na(cohort_new$race_new),]
#ethnicity regroup
cohort_new <- add_column(cohort_new, ethnicity_new = NA)
cohort_new[cohort_new$ethnicity %in% c("Not of Spanish/Hispanic Origin",
                                       "Not of Spanish/Hispanic Origin, Unknown"),]$ethnicity_new <- "Not Hispanic"
cohort_new[cohort_new$ethnicity %in% c("Patient Refused","Unknown",
                                       "Unknown, Not of Spanish/Hispanic Origin",NA),]$ethnicity_new <- "Unknown"
cohort_new[is.na(cohort_new$ethnicity_new),]$ethnicity_new <- "Hispanic"
cohort_new[is.na(cohort_new$ethnicity_new),]
cohort_new[is.na(cohort_new$race_new),]$race
cohort_new[is.na(cohort_new$ethnicity_new),]$ethnicity
```

(1) cohort (674, from 3-31 to 4-14): the age, gender, race and ethnicity, whether they live in the real world 

```{r}
a <- table(cohort_new$pat_id) > 1
more2 <- names(table(cohort_new$pat_id))[a]
s_date <- as.Date("2020-03-31",format = ("%Y-%m-%d"))
la_date <- as.Date("2020-04-14",format = ("%Y-%m-%d"))
v_date <- seq(s_date,la_date,by = 1)
group_all <- NULL
for (k in v_date) {
  c_df <- allo2 %>% filter(date == k)
  group_all <- unique(c(group_all,unique(c_df$pat_id)))
}
#enroll for once
group_all1 <- group_all[!group_all %in% more2] 
#enroll for several times
group_all2 <- group_all[group_all %in% more2] #15 patients
```


Age
```{r}
#age
#enroll for once
age_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$"age" 
#enroll for several times
#"Z8268782"
age_all2 <- NULL
d1 <- cohort_new[cohort_new$pat_id == "Z8268782",]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d1$"age"[1])
#"Z4356816" 
d2 <- cohort_new[cohort_new$pat_id == "Z4356816" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d2$"age"[2],d2$"age"[1])
#"Z634268"
d3 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d3$"age"[1])
#"Z1906509"
d4 <- cohort_new[cohort_new$pat_id == "Z1906509" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d4$"age"[1])
#"Z5874193"
d5 <- cohort_new[cohort_new$pat_id == "Z5874193",]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d5$"age"[1])
#"Z8138823"
d6 <- cohort_new[cohort_new$pat_id == "Z8138823",]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d6$"age"[1])
#"Z6223347"
d7 <- cohort_new[cohort_new$pat_id == "Z6223347",]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d7$"age"[2])
#"Z639784"
d8 <- cohort_new[cohort_new$pat_id == "Z639784",]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d8$"age"[2])
#"Z2173404"
d9 <- cohort_new[cohort_new$pat_id == "Z2173404",]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d9$"age"[2])
#"Z8223957"
d10 <- cohort_new[cohort_new$pat_id == "Z8223957",]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d10$"age"[2])
#Z3338372"
d11 <- cohort_new[cohort_new$pat_id == "Z3338372" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d11$"age"[1])
#"Z7002226"
d12 <- cohort_new[cohort_new$pat_id == "Z7002226" ,]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d12$"age"[2])
#"Z2417059"
d13 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d13$"age"[2])
#"Z8089628"
d14 <- cohort_new[cohort_new$pat_id == "Z8089628" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d14$"age"[1])
#Z2656846"
d15 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d15$"age"[1])
age_all <- c(age_all1,age_all2)
format(x = mean(age_all, na.rm = T),digits = 6)
format(sd(age_all, na.rm = T),digits = 6)
```

Gender
```{r}
#gender
#enroll for once
gender_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$sex
#enroll for several times
#"Z8268782"
gender_all2 <- NULL
d1 <- cohort_new[cohort_new$pat_id == "Z8268782",]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d1$"sex"[1])
#"Z4356816" 
d2 <- cohort_new[cohort_new$pat_id == "Z4356816" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d2$"sex"[2],d2$"sex"[1])
#"Z634268"
d3 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d3$"sex"[1])
#"Z1906509"
d4 <- cohort_new[cohort_new$pat_id == "Z1906509" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d4$"sex"[1])
#"Z5874193"
d5 <- cohort_new[cohort_new$pat_id == "Z5874193",]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d5$"sex"[1])
#"Z8138823"
d6 <- cohort_new[cohort_new$pat_id == "Z8138823",]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d6$"sex"[1])
#"Z6223347"
d7 <- cohort_new[cohort_new$pat_id == "Z6223347",]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d7$"sex"[2])
#"Z639784"
d8 <- cohort_new[cohort_new$pat_id == "Z639784",]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d8$"sex"[2])
#"Z2173404"
d9 <- cohort_new[cohort_new$pat_id == "Z2173404",]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d9$"sex"[2])
#"Z8223957"
d10 <- cohort_new[cohort_new$pat_id == "Z8223957",]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d10$"sex"[2])
#Z3338372"
d11 <- cohort_new[cohort_new$pat_id == "Z3338372" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d11$"sex"[1])
#"Z7002226"
d12 <- cohort_new[cohort_new$pat_id == "Z7002226" ,]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d12$"sex"[2])
#"Z2417059"
d13 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d13$"sex"[2])
#"Z8089628"
d14 <- cohort_new[cohort_new$pat_id == "Z8089628" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d14$"sex"[1])
#Z2656846"
d15 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d15$"sex"[1])
gender_all <- c(gender_all1,gender_all2)
t1 <- table(gender_all)
t1
t1/length(gender_all)
```

Race
```{r}
#race
#enroll for once
race_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$race_new
#enroll for several times
race_all2 <- NULL
d1 <- cohort_new[cohort_new$pat_id == "Z8268782",]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d1$"race_new"[1])
#"Z4356816" 
d2 <- cohort_new[cohort_new$pat_id == "Z4356816" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d2$"race_new"[2],d2$"race_new"[1])
#"Z634268"
d3 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d3$"race_new"[1])
#"Z1906509"
d4 <- cohort_new[cohort_new$pat_id == "Z1906509" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d4$"race_new"[1])
#"Z5874193"
d5 <- cohort_new[cohort_new$pat_id == "Z5874193",]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d5$"race_new"[1])
#"Z8138823"
d6 <- cohort_new[cohort_new$pat_id == "Z8138823",]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d6$"race_new"[1])
#"Z6223347"
d7 <- cohort_new[cohort_new$pat_id == "Z6223347",]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d7$"race_new"[2])
#"Z639784"
d8 <- cohort_new[cohort_new$pat_id == "Z639784",]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d8$"race_new"[2])
#"Z2173404"
d9 <- cohort_new[cohort_new$pat_id == "Z2173404",]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d9$"race_new"[2])
#"Z8223957"
d10 <- cohort_new[cohort_new$pat_id == "Z8223957",]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d10$"race_new"[2])
#Z3338372"
d11 <- cohort_new[cohort_new$pat_id == "Z3338372" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d11$"race_new"[1])
#"Z7002226"
d12 <- cohort_new[cohort_new$pat_id == "Z7002226" ,]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d12$"race_new"[2])
#"Z2417059"
d13 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d13$"race_new"[2])
#"Z8089628"
d14 <- cohort_new[cohort_new$pat_id == "Z8089628" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d14$"race_new"[1])
#Z2656846"
d15 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d15$"race_new"[1])
race_all <- c(race_all1,race_all2)
t2 <- table(race_all)
t2
t2/length(race_all)
```

Ethnicity
```{r}
#Ethnicity
#enroll for once
eth_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$ethnicity_new
#enroll for several times
eth_all2 <- NULL
d1 <- cohort_new[cohort_new$pat_id == "Z8268782",]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d1$"ethnicity_new"[1])
#"Z4356816" 
d2 <- cohort_new[cohort_new$pat_id == "Z4356816" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d2$"ethnicity_new"[2],d2$"ethnicity_new"[1])
#"Z634268"
d3 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d3$"ethnicity_new"[1])
#"Z1906509"
d4 <- cohort_new[cohort_new$pat_id == "Z1906509" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d4$"ethnicity_new"[1])
#"Z5874193"
d5 <- cohort_new[cohort_new$pat_id == "Z5874193",]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d5$"ethnicity_new"[1])
#"Z8138823"
d6 <- cohort_new[cohort_new$pat_id == "Z8138823",]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d6$"ethnicity_new"[1])
#"Z6223347"
d7 <- cohort_new[cohort_new$pat_id == "Z6223347",]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d7$"ethnicity_new"[2])
#"Z639784"
d8 <- cohort_new[cohort_new$pat_id == "Z639784",]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d8$"ethnicity_new"[2])
#"Z2173404"
d9 <- cohort_new[cohort_new$pat_id == "Z2173404",]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d9$"ethnicity_new"[2])
#"Z8223957"
d10 <- cohort_new[cohort_new$pat_id == "Z8223957",]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d10$"ethnicity_new"[2])
#Z3338372"
d11 <- cohort_new[cohort_new$pat_id == "Z3338372" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d11$"ethnicity_new"[1])
#"Z7002226"
d12 <- cohort_new[cohort_new$pat_id == "Z7002226" ,]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d12$"ethnicity_new"[2])
#"Z2417059"
d13 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d13$"ethnicity_new"[2])
#"Z8089628"
d14 <- cohort_new[cohort_new$pat_id == "Z8089628" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d14$"ethnicity_new"[1])
#Z2656846"
d15 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d15$"ethnicity_new"[1])
eth_all <- c(eth_all1,eth_all2)
t3 <- table(eth_all)
t3
t3/length(eth_all)
```

whether they live in the real world 
```{r}
#outcome
cohort_new[is.na(cohort_new$dead),]$dead <- 0
cohort_new$dead <- as.character(cohort_new$dead)
cohort_new[cohort_new$dead == "1",]$dead <- "deceased"
cohort_new[cohort_new$dead == "0",]$dead <- "alive"
outcome_all1 <- as.character(rep(0,length(group_all1)))
for (i in seq_along(group_all1)) {
  outcome_all1[i] <- cohort_new[cohort_new$pat_id == group_all1[i],]$"dead" 
}
outcome_all2 <- NULL
d1 <- cohort_new[cohort_new$pat_id == "Z8268782",]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d1$"dead"[1])
#"Z4356816" 
d2 <- cohort_new[cohort_new$pat_id == "Z4356816" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d2$"dead"[2],d2$"dead"[1])
#"Z634268"
d3 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d3$"dead"[1])
#"Z1906509"
d4 <- cohort_new[cohort_new$pat_id == "Z1906509" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d4$"dead"[1])
#"Z5874193"
d5 <- cohort_new[cohort_new$pat_id == "Z5874193",]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d5$"dead"[1])
#"Z8138823"
d6 <- cohort_new[cohort_new$pat_id == "Z8138823",]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d6$"dead"[1])
#"Z6223347"
d7 <- cohort_new[cohort_new$pat_id == "Z6223347",]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d7$"dead"[2])
#"Z639784"
d8 <- cohort_new[cohort_new$pat_id == "Z639784",]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d8$"dead"[2])
#"Z2173404"
d9 <- cohort_new[cohort_new$pat_id == "Z2173404",]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d9$"dead"[2])
#"Z8223957"
d10 <- cohort_new[cohort_new$pat_id == "Z8223957",]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d10$"dead"[2])
#Z3338372"
d11 <- cohort_new[cohort_new$pat_id == "Z3338372" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d11$"dead"[1])
#"Z7002226"
d12 <- cohort_new[cohort_new$pat_id == "Z7002226" ,]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d12$"dead"[2])
#"Z2417059"
d13 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d13$"dead"[2])
#"Z8089628"
d14 <- cohort_new[cohort_new$pat_id == "Z8089628" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d14$"dead"[1])
#Z2656846"
d15 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d15$"dead"[1])
outcome_all <- c(outcome_all1, outcome_all2)
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

(2) group_give

average and the sd of the number

```{r}
length1 = rep(0,length(group_give_all))
for (i in seq_along(group_give_all)) {
  length1[i] = nrow(group_give_all[[i]])
}
mean(length1)
sd(length1)
```


for each simulation
```{r}
mean_groupa <- rep(0,length(group_give_all))
sd_groupa <- rep(0,length(group_give_all))
gender_percent_groupa <- 0
gender_number_groupa <- 0
race_percent_groupa <- NULL
race_number_groupa <- NULL
ethnicity_percent_groupa <- NULL
ethnicity_number_groupa <- NULL
outcome_percent_groupa <- NULL
outcome_number_groupa <- NULL
for (j in seq_along(group_give_all)) {
  #cat("i = ", j, "\n")
groupa <- group_give_all[[j]]$pat_enc_csn_id
groupa_id <- group_give_all[[j]]$pat_id
#AGE
age_groupa <- rep(0,length(groupa))
for (i in 1:length(groupa)) {
age_groupa[i] <- max(cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$"age")
}
mean_groupa[j] <- mean(age_groupa,na.rm = T)
sd_groupa[j] <- sd(age_groupa,na.rm = T) 
#GENDER
gender_groupa <- rep(0,length(groupa))
for (i in 1:length(groupa)) {
 gender_groupa[i] <- unique(cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$sex)
}
t1 <- table(gender_groupa)
gender_percent_groupa <- t1/length(groupa) + gender_percent_groupa
gender_number_groupa <- t1 + gender_number_groupa
#RACE
race_groupa <- rep(0,length(groupa))
for (i in 1:length(groupa)) {
 race_groupa[i] <- unique(cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$race_new)
}
t2 <- table(race_groupa)
race_percent_groupa[[j]] <- t2/length(groupa)
race_number_groupa[[j]] <- t2
#ETHNICITY
eth_groupa <- rep(0,length(groupa))
for (i in 1:length(groupa)) {
 eth_groupa[i] <- unique(cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$ethnicity_new)
}
t3 <- table(eth_groupa)
ethnicity_percent_groupa[[j]] <- t3/length(groupa)
ethnicity_number_groupa[[j]] <- t3
#OUTCOME
middle <- NULL
outcome_groupa <- as.character(rep(0,length(groupa_id)))
for (i in seq_along(groupa)) {
  middle[[i]] <- cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$"dead"
  if(sum(middle[[i]] %in% "deceased") > 0){
    outcome_groupa[i] <- "deceased" 
  } else {
    outcome_groupa[i] <- "alive" 
  }
}
t4 <- table(outcome_groupa)
outcome_percent_groupa[[j]] <- t4/length(groupa_id)
outcome_number_groupa[[j]] <- t4
}

```

allocation score
```{r}
score_bl <- NULL
for (i in seq_along(group_give_all)) {
  score_bl[[i]] <- group_give_all[[i]]$`Cali-psN`
}
summary(sapply(score_bl, mean))
#the sd
sd(sapply(score_bl, mean))
```

the day - group a
```{r}
day_bl <- NULL
for (i in seq_along(group_give_all)) {
  day_bl[[i]] <- group_give_all[[i]]$intubated_day
}
summary(sapply(day_bl, mean))
```

age
```{r}
mean(mean_groupa) #mean
mean(sd_groupa) #sd
```

gender
```{r}
gender_number_groupa/length(group_give_all)
gender_percent_groupa/length(group_give_all)
```

race
```{r}
race_percent <- rep(0,5)
race_number <- rep(0,5)
names(race_percent) <- names(race_number) <- c("African American","Asian","Unknown","White","Native American")
for (j in seq_along(race_percent_groupa)) {
race_percent["African American"] <- race_percent["African American"] + race_percent_groupa[[j]]["African American"]
race_percent["Asian"] <- race_percent["Asian"] + race_percent_groupa[[j]]["Asian"]
race_percent["Unknown"] <- race_percent["Unknown"] + race_percent_groupa[[j]]["Unknown"]
race_percent["White"] <- race_percent["White"] + race_percent_groupa[[j]]["White"]
if(!is.na(race_percent_groupa[[j]]["Native American"])){
race_percent["Native American"] <- race_percent["Native American"] + race_percent_groupa[[j]]["Native American"]
}
race_number["African American"] <- race_number["African American"] + race_number_groupa[[j]]["African American"]
race_number["Asian"] <- race_number["Asian"] + race_number_groupa[[j]]["Asian"]
race_number["Unknown"] <- race_number["Unknown"] + race_number_groupa[[j]]["Unknown"]
race_number["White"] <- race_number["White"] + race_number_groupa[[j]]["White"]
if(!is.na(race_number_groupa[[j]]["Native American"])){
race_number["Native American"] <- race_number["Native American"] + race_number_groupa[[j]]["Native American"]
}
}
race_number/length(group_give_all)
race_percent/length(group_give_all)
```

ethnicity
```{r}
ethnicity_percent <- rep(0,3)
ethnicity_number <- rep(0,3)
names(ethnicity_percent) <- names(ethnicity_number) <- c("Hispanic","Not Hispanic","Unknown")
for (j in seq_along(ethnicity_percent_groupa)) {
ethnicity_percent["Hispanic"] <- ethnicity_percent["Hispanic"] + ethnicity_percent_groupa[[j]]["Hispanic"]
ethnicity_percent["Not Hispanic"] <- ethnicity_percent["Not Hispanic"] + ethnicity_percent_groupa[[j]]["Not Hispanic"]
if(!is.na(ethnicity_percent_groupa[[j]]["Unknown"])){
ethnicity_percent["Unknown"] <- ethnicity_percent["Unknown"] + ethnicity_percent_groupa[[j]]["Unknown"]
}

ethnicity_number["Hispanic"] <- ethnicity_number["Hispanic"] + ethnicity_number_groupa[[j]]["Hispanic"]
ethnicity_number["Not Hispanic"] <- ethnicity_number["Not Hispanic"] + ethnicity_number_groupa[[j]]["Not Hispanic"]
if(!is.na(ethnicity_number_groupa[[j]]["Unknown"])){
ethnicity_number["Unknown"] <- ethnicity_number["Unknown"] + ethnicity_number_groupa[[j]]["Unknown"]
}
}
ethnicity_number/length(group_give_all)
ethnicity_percent/length(group_give_all)
```

outcome
```{r}
outcome_percent <- rep(0,2)
outcome_number <- rep(0,2)
names(outcome_percent) <- names(outcome_number) <- c("alive","deceased")
for (j in seq_along(ethnicity_percent_groupa)) {
outcome_percent["alive"] <- outcome_percent["alive"] + outcome_percent_groupa[[j]]["alive"]
outcome_percent["deceased"] <- outcome_percent["deceased"] + outcome_percent_groupa[[j]]["deceased"]

outcome_number["alive"] <- outcome_number["alive"] + outcome_number_groupa[[j]]["alive"]
outcome_number["deceased"] <- outcome_number["deceased"] + outcome_number_groupa[[j]]["deceased"]
}
outcome_percent/length(group_give_all)
#sd of the percentage of the outcome
sd1 = rep(0,length(ethnicity_percent_groupa))
for (j in seq_along(ethnicity_percent_groupa)) {
sd1[j] =  outcome_percent_groupa[[j]]["alive"]
}
sd(sd1)
outcome_number/length(group_give_all)
#sd of the number of the outcome
sd2 = rep(0,length(ethnicity_percent_groupa))
for (j in seq_along(ethnicity_percent_groupa)) {
sd2[j] =  outcome_number_groupa[[j]]["alive"]
}
sd(sd2)
```

(3) group_receive

average and the sd of the number

```{r}
length2 = rep(0,length(group_receive_all))
for (i in seq_along(group_receive_all)) {
  length2[i] = nrow(group_receive_all[[i]])
}
mean(length2)
sd(length2)
```


for each simulation
```{r}
mean_groupb <- rep(0,length(group_receive_all))
sd_groupb <- rep(0,length(group_receive_all))
gender_percent_groupb <- 0
gender_number_groupb <- 0
race_percent_groupb <- NULL
race_number_groupb <- NULL
ethnicity_percent_groupb <- NULL
ethnicity_number_groupb <- NULL
outcome_percent_groupb <- NULL
outcome_number_groupb <- NULL
for (j in seq_along(group_receive_all)) {
  #cat("i = ", j, "\n")
groupb_15 <- group_receive_all[[j]]$pat_enc_csn_id
groupb_15_id <- group_receive_all[[j]]$pat_id
#AGE
age_groupb <- rep(0,length(groupb_15))
for (i in 1:length(groupb_15)) {
age_groupb[i] <- max(cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$"age")
}
mean_groupb[j] <- mean(age_groupb,na.rm = T)
sd_groupb[j] <- sd(age_groupb,na.rm = T) 
#GENDER
gender_groupb <- rep(0,length(groupb_15))
for (i in 1:length(groupb_15)) {
 gender_groupb[i] <- unique(cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$sex)
}
t1 <- table(gender_groupb)
gender_percent_groupb <- t1/length(groupb_15) + gender_percent_groupb
gender_number_groupb <- t1 + gender_number_groupb
#RACE
race_groupb <- rep(0,length(groupb_15))
for (i in 1:length(groupb_15)) {
 race_groupb[i] <- unique(cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$race_new)
}
t2 <- table(race_groupb)
race_percent_groupb[[j]] <- t2/length(groupb_15)
race_number_groupb[[j]] <- t2
#ETHNICITY
eth_groupb <- rep(0,length(groupb_15))
for (i in 1:length(groupb_15)) {
 eth_groupb[i] <- unique(cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$ethnicity_new)
}
t3 <- table(eth_groupb)
ethnicity_percent_groupb[[j]] <- t3/length(groupb_15)
ethnicity_number_groupb[[j]] <- t3
#OUTCOME
middle <- NULL
outcome_groupb <- as.character(rep(0,length(groupb_15_id)))
for (i in seq_along(groupb_15)) {
  middle[[i]] <- cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$"dead"
  if(sum(middle[[i]] %in% "deceased") > 0){
    outcome_groupb[i] <- "deceased" 
  } else {
    outcome_groupb[i] <- "alive" 
  }
}
t4 <- table(outcome_groupb)
outcome_percent_groupb[[j]] <- t4/length(groupb_15_id)
outcome_number_groupb[[j]] <- t4
}
```

allocation score
```{r}
score_bl <- NULL
for (i in seq_along(group_receive_all)) {
  score_bl[[i]] <- group_receive_all[[i]]$`Cali-psN`
}
summary(sapply(score_bl, mean))
#the sd
sd(sapply(score_bl, mean))
```



age
```{r}
mean(mean_groupb) #mean
mean(sd_groupb) #sd
```
gender
```{r}
gender_number_groupb/length(group_receive_all)
gender_percent_groupb/length(group_receive_all)
```

race
```{r}
race_percent <- rep(0,5)
race_number <- rep(0,5)
names(race_percent) <- names(race_number) <- c("African American","Asian","Unknown","White","Native American")
for (j in seq_along(race_percent_groupb)) {
race_percent["African American"] <- race_percent["African American"] + race_percent_groupb[[j]]["African American"]
race_percent["Asian"] <- race_percent["Asian"] + race_percent_groupb[[j]]["Asian"]
race_percent["Unknown"] <- race_percent["Unknown"] + race_percent_groupb[[j]]["Unknown"]
race_percent["White"] <- race_percent["White"] + race_percent_groupb[[j]]["White"]
if(!is.na(race_percent_groupb[[j]]["Native American"])){
race_percent["Native American"] <- race_percent["Native American"] + race_percent_groupb[[j]]["Native American"]
}
race_number["African American"] <- race_number["African American"] + race_number_groupb[[j]]["African American"]
race_number["Asian"] <- race_number["Asian"] + race_number_groupb[[j]]["Asian"]
race_number["Unknown"] <- race_number["Unknown"] + race_number_groupb[[j]]["Unknown"]
race_number["White"] <- race_number["White"] + race_number_groupb[[j]]["White"]
if(!is.na(race_number_groupb[[j]]["Native American"])){
race_number["Native American"] <- race_number["Native American"] + race_number_groupb[[j]]["Native American"]
}
}
race_number/length(group_receive_all)
race_percent/length(group_receive_all)
```

ethnicity
```{r}
ethnicity_percent <- rep(0,3)
ethnicity_number <- rep(0,3)
names(ethnicity_percent) <- names(ethnicity_number) <- c("Hispanic","Not Hispanic","Unknown")
for (j in seq_along(ethnicity_percent_groupb)) {
ethnicity_percent["Hispanic"] <- ethnicity_percent["Hispanic"] + ethnicity_percent_groupb[[j]]["Hispanic"]
ethnicity_percent["Not Hispanic"] <- ethnicity_percent["Not Hispanic"] + ethnicity_percent_groupb[[j]]["Not Hispanic"]
if(!is.na(ethnicity_percent_groupb[[j]]["Unknown"])){
ethnicity_percent["Unknown"] <- ethnicity_percent["Unknown"] + ethnicity_percent_groupb[[j]]["Unknown"]
}

ethnicity_number["Hispanic"] <- ethnicity_number["Hispanic"] + ethnicity_number_groupb[[j]]["Hispanic"]
ethnicity_number["Not Hispanic"] <- ethnicity_number["Not Hispanic"] + ethnicity_number_groupb[[j]]["Not Hispanic"]
if(!is.na(ethnicity_number_groupb[[j]]["Unknown"])){
ethnicity_number["Unknown"] <- ethnicity_number["Unknown"] + ethnicity_number_groupb[[j]]["Unknown"]
}

}
ethnicity_number/length(group_receive_all)
ethnicity_percent/length(group_receive_all)
```


outcome
```{r}
outcome_percent <- rep(0,2)
outcome_number <- rep(0,2)
names(outcome_percent) <- names(outcome_number) <- c("alive","deceased")
for (j in seq_along(ethnicity_percent_groupb)) {
outcome_percent["alive"] <- outcome_percent["alive"] + outcome_percent_groupb[[j]]["alive"]
outcome_percent["deceased"] <- outcome_percent["deceased"] + outcome_percent_groupb[[j]]["deceased"]

outcome_number["alive"] <- outcome_number["alive"] + outcome_number_groupb[[j]]["alive"]
outcome_number["deceased"] <- outcome_number["deceased"] + outcome_number_groupb[[j]]["deceased"]
}
outcome_percent/length(group_receive_all)
#sd of the percentage of the outcome
sd1 = rep(0,length(ethnicity_percent_groupa))
for (j in seq_along(ethnicity_percent_groupa)) {
sd1[j] =  outcome_percent_groupb[[j]]["alive"]
}
sd(sd1)
outcome_number/length(group_receive_all)
#sd of the number of the outcome
sd2 = rep(0,length(ethnicity_percent_groupa))
for (j in seq_along(ethnicity_percent_groupa)) {
sd2[j] =  outcome_number_groupb[[j]]["alive"]
}
sd(sd2)
```

(4) Moderate comorbidity


```{r}
mo_cor <- cohort_new[cohort_new$moderate_comor == 1 & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]
mo_cor <- mo_cor[!is.na(mo_cor$pat_enc_csn_id),]
#enroll for once
group_all1 <- mo_cor$pat_id[!mo_cor$pat_id %in% more2] 
#enroll for several times
group_all2 <- mo_cor$pat_id[mo_cor$pat_id %in% more2]  #4 patients
```


Age
```{r}
#age
#enroll for once
age_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$"age" 
#enroll for several times
#"Z634268"
d1 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d1$"age"[1])
#"Z2656846"
d2 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d2$"age"[2])
#Z2417059"
d3 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d3$"age"[2])
#Z6223347"
d4 <- cohort_new[cohort_new$pat_id == "Z6223347" ,]
#only the first admission contains the crisis period
age_all2 <- c(age_all2,d4$"age"[2])
age_all <- c(age_all1,age_all2)
format(x = mean(age_all, na.rm = T),digits = 6)
format(sd(age_all, na.rm = T),digits = 6)
```

Gender
```{r}
#gender
#enroll for once
gender_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$sex
#enroll for several times
gender_all2 <- NULL
#"Z634268"
d1 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d1$sex[1])
#"Z2656846"
d2 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d2$sex[2])
#Z2417059"
d3 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d3$sex[2])
#Z6223347"
d4 <- cohort_new[cohort_new$pat_id == "Z6223347" ,]
#only the first admission contains the crisis period
gender_all2 <- c(gender_all2,d4$sex[2])
gender_all <- c(gender_all1,gender_all2)
t1 <- table(gender_all)
t1
t1/length(gender_all)
```

Race
```{r}
#race
#enroll for once
race_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$race_new
#enroll for several times
race_all2 <- NULL
#"Z634268"
d1 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d1$race_new[1])
#"Z2656846"
d2 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d2$race_new[2])
#Z2417059"
d3 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d3$race_new[2])
#Z6223347"
d4 <- cohort_new[cohort_new$pat_id == "Z6223347" ,]
#only the first admission contains the crisis period
race_all2 <- c(race_all2,d4$race_new[2])
race_all <- c(race_all1,race_all2)
t2 <- table(race_all)
t2
t2/length(race_all)
```

Ethnicity
```{r}
#Ethnicity
#enroll for once
eth_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$ethnicity_new
#enroll for several times
eth_all2 <- NULL
#"Z634268"
d1 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d1$ethnicity_new[1])
#"Z2656846"
d2 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d2$ethnicity_new[2])
#Z2417059"
d3 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d3$ethnicity_new[2])
#Z6223347"
d4 <- cohort_new[cohort_new$pat_id == "Z6223347" ,]
#only the first admission contains the crisis period
eth_all2 <- c(eth_all2,d4$ethnicity_new[2])
eth_all <- c(eth_all1,eth_all2)
t3 <- table(eth_all)
t3
t3/length(eth_all)
```

whether they live in the real world (Pre-allocation)
```{r}
#outcome
outcome_all1 <- as.character(rep(0,length(group_all1)))
for (i in seq_along(group_all1)) {
  outcome_all1[i] <- cohort_new[cohort_new$pat_id == group_all1[i],]$"dead" 
}
outcome_all2 <- NULL
#"Z634268"
d1 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d1$"dead"[1])
#"Z2656846"
d2 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d2$"dead"[1])
#Z2417059"
d3 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d3$"dead"[2])
#Z6223347"
d4 <- cohort_new[cohort_new$pat_id == "Z6223347" ,]
#only the first admission contains the crisis period
outcome_all2 <- c(outcome_all2,d4$"dead"[2])
outcome_all <- c(outcome_all1, outcome_all2)
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

whether they live in the real world (Post-allocation)
```{r}
post_rate <- rep(0,10000)
for (i in 1:10000) {
  #cat("seed = ", i, "\n")
  outcome_all1 <- rep("deceased",length(group_all1))
  adf_id <- unique(allo3_all[[i]]$pat_id)
  id_live <- group_all1[group_all1 %in% adf_id] #except "Z1390418"
#outcome
  outcome_all1[1:length(id_live)] <- cohort_new[cohort_new$pat_id %in% id_live,]$"dead"
  outcome_all2 <- rep("deceased",4)
  if("Z634268" %in% id_live){
    d1 <- cohort_new[cohort_new$pat_id == "Z634268" ,]
    outcome_all2[1] <- d1$"dead"[1]
  }
  if("Z2656846" %in% id_live){
    d2 <- cohort_new[cohort_new$pat_id == "Z2656846" ,]
    outcome_all2[2] <- d2$"dead"[1]
  }
  if("Z2417059" %in% id_live){
    d3 <- cohort_new[cohort_new$pat_id == "Z2417059" ,]
    outcome_all2[3] <- d3$"dead"[2]
  }
  if("Z6223347" %in% id_live){
    d4 <- cohort_new[cohort_new$pat_id == "Z6223347" ,]
    outcome_all2[4] <- d4$"dead"[2]
  }
  outcome_all <- c(outcome_all1, outcome_all2)
  post_rate[i] <- (table(outcome_all)/length(outcome_all))[1]
}
mean(post_rate)
sd(post_rate)
```

how many patients were part of group_give

```{r}
n_give <- NULL
for (i in 1:10000) {
  group_all <- c(group_all1,group_all2)
  g_id <- group_give_all[[i]]$pat_id
  n_give <- c(n_give,sum(group_all %in% g_id))
}
mean(n_give)
sd(n_give)
```


(4) Severe comorbidity

```{r}
se_cor <- cohort_new[cohort_new$severe_comor == 1 & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]
se_cor <- se_cor[!is.na(se_cor$pat_enc_csn_id),]
#enroll for once
group_all1 <- se_cor$pat_id[!se_cor$pat_id %in% more2] 
#enroll for several times
group_all2 <- se_cor$pat_id[se_cor$pat_id %in% more2]  #1 patient
```


Age
```{r}
#age
#enroll for once
age_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$"age" 
#enroll for several times
#"Z8138823"
d1 <- cohort_new[cohort_new$pat_id == "Z8138823" ,]
#only the second admission contains the crisis period
age_all2 <- c(age_all2,d1$"age"[1])
age_all <- c(age_all1,age_all2)
format(x = mean(age_all, na.rm = T),digits = 6)
format(sd(age_all, na.rm = T),digits = 6)
```

Gender
```{r}
#gender
#enroll for once
gender_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$sex
#enroll for several times
gender_all2 <- NULL
#"Z8138823"
d1 <- cohort_new[cohort_new$pat_id == "Z8138823" ,]
#only the second admission contains the crisis period
gender_all2 <- c(gender_all2,d1$sex[1])
gender_all <- c(gender_all1,gender_all2)
t1 <- table(gender_all)
t1
t1/length(gender_all)
```

Race
```{r}
#race
#enroll for once
race_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$race_new
#enroll for several times
race_all2 <- NULL
#"Z8138823"
d1 <- cohort_new[cohort_new$pat_id == "Z8138823" ,]
#only the second admission contains the crisis period
race_all2 <- c(race_all2,d1$race_new[1])
race_all <- c(race_all1,race_all2)
t2 <- table(race_all)
t2
t2/length(race_all)
```

Ethnicity
```{r}
#Ethnicity
#enroll for once
eth_all1 <- cohort_new[cohort_new$pat_id %in% group_all1,]$ethnicity_new
#enroll for several times
eth_all2 <- NULL
#"Z8138823"
d1 <- cohort_new[cohort_new$pat_id == "Z8138823" ,]
#only the second admission contains the crisis period
eth_all2 <- c(eth_all2,d1$ethnicity_new[1])
eth_all <- c(eth_all1,eth_all2)
t3 <- table(eth_all)
t3
t3/length(eth_all)
```

whether they live in the real world (Pre-allocation)
```{r}
#outcome
outcome_all1 <- as.character(rep(0,length(group_all1)))
for (i in seq_along(group_all1)) {
  outcome_all1[i] <- cohort_new[cohort_new$pat_id == group_all1[i],]$"dead" 
}
outcome_all2 <- NULL
#"Z8138823"
d1 <- cohort_new[cohort_new$pat_id == "Z8138823" ,]
#only the second admission contains the crisis period
outcome_all2 <- c(outcome_all2,d1$"dead"[1])
outcome_all <- c(outcome_all1, outcome_all2)
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

whether they live in the real world (Post-allocation)
```{r}
post_rate <- rep(0,10000)
for (i in 1:10000) {
  #cat("seed = ", i, "\n")
  outcome_all1 <- rep("deceased",length(group_all1))
  adf_id <- unique(allo3_all[[i]]$pat_id)
  id_live <- group_all1[group_all1 %in% adf_id] 
#outcome
  if(length(id_live) == 0){
    outcome_all1 <- outcome_all1
  } else {
    outcome_all1[1:length(id_live)] <- cohort_new[cohort_new$pat_id %in% id_live,]$"dead"
  }
  outcome_all2 <- "deceased"
  if("Z8138823" %in% id_live){
    d1 <- cohort_new[cohort_new$pat_id == "Z8138823" ,]
    outcome_all2 <- d1$"dead"[1]
  }
  outcome_all <- c(outcome_all1, outcome_all2)
  post_rate[i] <- table(outcome_all)["alive"]/length(outcome_all)
}

post_rate[is.na(post_rate)] <- 0
mean(post_rate)
sd(post_rate)
```

how many patients were part of group_give

```{r}
n_give <- NULL
for (i in 1:10000) {
  group_all <- c(group_all1,group_all2)
  g_id <- group_give_all[[i]]$pat_id
  n_give <- c(n_give,sum(group_all %in% g_id))
}
mean(n_give)
sd(n_give)
```



(5) Pregnancy

```{r}
preg <- cohort_new[cohort_new$pregnant == 1 & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]
preg <- preg[!is.na(preg$pat_enc_csn_id),]
#enroll for once
group_all1 <- preg$pat_id[!preg$pat_id %in% more2] 
#enroll for several times
group_all2 <- preg$pat_id[preg$pat_id %in% more2]  #0 patient
```


Age
```{r}
#age
#enroll for once
age_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$"age" 
format(x = mean(age_all, na.rm = T),digits = 6)
format(sd(age_all, na.rm = T),digits = 6)
```

Gender
```{r}
#gender
#enroll for once
gender_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$sex
t1 <- table(gender_all)
t1
t1/length(gender_all)
```

Race
```{r}
#race
#enroll for once
race_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$race_new
t2 <- table(race_all)
t2
t2/length(race_all)
```

Ethnicity
```{r}
#Ethnicity
#enroll for once
eth_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$ethnicity_new
t3 <- table(eth_all)
t3
t3/length(eth_all)
```

whether they live in the real world (Pre-allocation)
```{r}
#outcome
outcome_all <- as.character(rep(0,length(group_all1)))
for (i in seq_along(group_all1)) {
  outcome_all[i] <- cohort_new[cohort_new$pat_id == group_all1[i],]$"dead" 
}
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

whether they live in the real world (Post-allocation)
```{r}
adf_id <- unique(allo2$pat_id)
id_live <- group_all1[group_all1 %in% adf_id] #all
#outcome
outcome_all <- as.character(rep(0,length(id_live)))
for (i in seq_along(id_live)) {
  outcome_all[i] <- cohort_new[cohort_new$pat_id == id_live[i],]$"dead" 
}
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

(6) non-transplant

```{r}
non_trans <- cohort_new[cohort_new$non_transplant == 1 & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]
non_trans <- non_trans[!is.na(non_trans$pat_enc_csn_id),]
#enroll for once
group_all1 <- non_trans$pat_id[!non_trans$pat_id %in% more2] 
#enroll for several times
group_all2 <- non_trans$pat_id[non_trans$pat_id %in% more2]  #0 patient
```


Age
```{r}
#age
#enroll for once
age_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$"age" 
format(x = mean(age_all, na.rm = T),digits = 6)
format(sd(age_all, na.rm = T),digits = 6)
```

Gender
```{r}
#gender
#enroll for once
gender_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$sex
t1 <- table(gender_all)
t1
t1/length(gender_all)
```

Race
```{r}
#race
#enroll for once
race_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$race_new
t2 <- table(race_all)
t2
t2/length(race_all)
```

Ethnicity
```{r}
#Ethnicity
#enroll for once
eth_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$ethnicity_new
t3 <- table(eth_all)
t3
t3/length(eth_all)
```

whether they live in the real world (Pre-allocation)
```{r}
#outcome
outcome_all <- as.character(rep(0,length(group_all1)))
for (i in seq_along(group_all1)) {
  outcome_all[i] <- cohort_new[cohort_new$pat_id == group_all1[i],]$"dead" 
}
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

whether they live in the real world (Post-allocation)
```{r}
adf_id <- unique(allo2$pat_id)
id_live <- group_all1[group_all1 %in% adf_id] #all
#outcome
outcome_all <- as.character(rep(0,length(id_live)))
for (i in seq_along(id_live)) {
  outcome_all[i] <- cohort_new[cohort_new$pat_id == id_live[i],]$"dead" 
}
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

(7) transplant

```{r}
trans <- cohort_new[cohort_new$transplant == 1 & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]
trans <- trans[!is.na(trans$pat_enc_csn_id),]
#enroll for once
group_all1 <- trans$pat_id[!trans$pat_id %in% more2] 
#enroll for several times
group_all2 <- trans$pat_id[trans$pat_id %in% more2]  #0 patient
```


Age
```{r}
#age
#enroll for once
age_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$"age" 
format(x = mean(age_all, na.rm = T),digits = 6)
```

Gender
```{r}
#gender
#enroll for once
gender_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$sex
t1 <- table(gender_all)
t1
t1/length(gender_all)
```

Race
```{r}
#race
#enroll for once
race_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$race_new
t2 <- table(race_all)
t2
t2/length(race_all)
```

Ethnicity
```{r}
#Ethnicity
#enroll for once
eth_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$ethnicity_new
t3 <- table(eth_all)
t3
t3/length(eth_all)
```

whether they live in the real world (Pre-allocation)
```{r}
#outcome
outcome_all <- as.character(rep(0,length(group_all1)))
for (i in seq_along(group_all1)) {
  outcome_all[i] <- cohort_new[cohort_new$pat_id == group_all1[i],]$"dead" 
}
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

whether they live in the real world (Post-allocation)
```{r}
adf_id <- unique(allo2$pat_id)
id_live <- group_all1[group_all1 %in% adf_id] #all
#outcome
outcome_all <- as.character(rep(0,length(id_live)))
for (i in seq_along(id_live)) {
  outcome_all[i] <- cohort_new[cohort_new$pat_id == id_live[i],]$"dead" 
}
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```

(8) critical workers

```{r}
pre <- allo2[allo2$worker == 1 & allo2$date >= "2020-03-31" & allo2$date <= "2020-04-14",]
```

age
```{r}
pre_id <- unique(pre$pat_enc_csn_id)
age_ex <- mean(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"age")
sd_ex <- sd(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"age")
#mean
age_ex
#sd
sd_ex
```


sex
```{r}
pre_id <- unique(pre$pat_enc_csn_id)
sex_ex <- table(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"sex")
sex_ex_p <- table(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"sex")/length(pre_id)
sex_ex
sex_ex_p
```

race
```{r}
pre_id <- unique(pre$pat_enc_csn_id)
race_ex <- table(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"race_new")
race_ex_p <- table(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"race_new")/length(pre_id)
race_ex
race_ex_p
```

ethnicity
```{r}
pre_id <- unique(pre$pat_enc_csn_id)
eth_ex <- table(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"ethnicity_new")
eth_ex_p <- table(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"ethnicity_new")/length(pre_id)
eth_ex
eth_ex_p
```

outcome
```{r}
pre_id <- unique(pre$pat_enc_csn_id)
dead_ex <- table(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"dead")
dead_ex_p <- table(cohort_new[cohort_new$pat_enc_csn_id %in% pre_id,]$"dead")/length(pre_id) 
dead_ex
dead_ex_p
```





