---
title: "maryland_results"
author: "Jianan"
date: "2023-04-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(readxl)
library(tibble)
library(purrr)
library(plyr)
```


load the 100 simulations
```{r}
load("ventilator_maryland.RData")
load("date.RData")
load("dataset.RData")
```

(1) start date of the crisis period
```{r}
table(start_date)
```

(2) last_date of the crisis period
```{r}
table(last_date)
```

(3) number of days between start & end of crisis period
```{r}
table(total)
```

(4) total number of patients after allocation for each day

```{r}
t = total == 15
options(digits = 3)
v_all_15 <- v_all[t]
sum_v <- rep(0, length(v_all_15[[1]]))
for(i in 1:length(v_all_15)){
  sum_v <- sum_v + v_all_15[[i]]
}
n2 <- sum_v/length(v_all_15)
names(n2) <- d
n2
```


(5) standard deviation of the total number of patients after allocation for each day


```{r}
options(digits = 3)
t = total == 15
v_all_15 <- v_all[t]
v_all_sd <- sapply(1:length(v_all_15[[1]]), function(j){sd(v_all_15 %>% map_dbl(c(j)))})
names(v_all_sd) <-d 
v_all_sd
```


(6) survival rate for the cohort (post-allocation)

```{r}
cohort_new[is.na(cohort_new$dead),]$dead <- 0
cohort_new$dead <- as.character(cohort_new$dead)
cohort_new[cohort_new$dead == "1",]$dead <- "deceased"
cohort_new[cohort_new$dead == "0",]$dead <- "alive"
options(digits = 3)
t = total == 15
sofa3_all_15 <- sofa3_all[t]
survival <- 0
for (i in 1:length(sofa3_all_15)) {
  cohort <- sofa3_all_15[[i]][sofa3_all_15[[i]]$date >= "2020-03-31" & sofa3_all_15[[i]]$date <= "2020-04-14",]
  id <- unique(cohort$pat_enc_csn_id)
  survival <- table(cohort_new[cohort_new$pat_enc_csn_id %in% id,]$dead)[1]/675 + survival
}
survival/length(sofa3_all_15)
```

(7) survival rate for group——give 

```{r}
t = total == 15
group_give_all_15 <- group_give_all[t]
a <- 0
for (i in 1:length(group_give_all_15)) {
  id <- group_give_all_15[[i]]$pat_enc_csn_id
  a <- table(cohort_new[cohort_new$pat_enc_csn_id %in% id,]$dead)[1]/length(id) + a
}
format(a/length(group_give_all_15),digits = 5)
```

(8) survival rate for group--receive

```{r}
t = total == 15
group_receive_all_15 <- group_receive_all[t]
b <- 0
for (i in 1:length(group_receive_all_15)) {
  id <- group_receive_all_15[[i]]$pat_enc_csn_id
  b <- table(cohort_new[cohort_new$pat_enc_csn_id %in% id,]$dead)[1]/length(id) + b
}
format(b/length(group_receive_all_15),digits = 5)
```


```{r include = FALSE}
#race regroup
cohort_new <- add_column(cohort_new, race_new = NA)
cohort_new[cohort_new$race %in% c("White","Unknown, White",
                                  "Other Race, White","White, Other Race",
                                  "White, Unknown",
                                  "White, Other Pacific Islander",
                                  "White;Other Race",
                                  "White;Other Race",
                                  "Patient Refused;White",
                                  "Other Race;White"),]$race_new <- "White"
cohort_new[cohort_new$race %in% c("African American (Black)",
                                  "African American (Black), White",
                                  "African American (Black), Bangladeshi",
                                  "Chinese;African American (Black)",
                                  "White;African American (Black)",
                                  "Bangladeshi;African American (Black)"),]$race_new <- "African American"
cohort_new[cohort_new$race %in% c("Asian","Chinese","Chinese, Asian - unspecified","Japanese",
                                  "Pakistani","Bangladeshi","Asian - unspecified, Other Race",
                                  "Korean, Unknown","Other Pacific Islander","Asian Indian",
                                  "Asian - unspecified","Unknown, Chinese","Chinese, Other Race",
                                  "Filipino","Filipino, Other Pacific Islander",
                                  "Other Race, Chinese",
                                  "Asian;Asian - unspecified",
                                  "Korean","Other Race;Chinese",
                                  "Chinese;Asian - unspecified",
                                  "Vietnamese","Asian Indian;Other Race",
                                  "Asian - unspecified;Chinese",
                                  "Chinese;Asian"),]$race_new <- "Asian"
cohort_new[cohort_new$race %in% c("Native American (American Indian/Eskimo/Aleutian)",
                                  "Native American (American Indian/Eskimo/Aleutian) , Other Pacific Islander",
                                  "White;Native American (American Indian/Eskimo/Aleutian)",
                                  "Other Pacific Islander;Native American (American Indian/Eskimo/Aleutian)",
                                  "Native American (American Indian/Eskimo/Aleutian) ;African American (Black)",
                                  "Other Pacific Islander;White",
                                  "Filipino;Other Pacific Islander",
                                  "Native American (American Indian/Eskimo/Aleutian) ;African American (Black)"),]$race_new <- "Native American"
cohort_new[cohort_new$race %in% c("Unknown","Other Race",NA,"Patient Refused",
                                  "Unknown, Other Race","Other Race, Unknown","0"),]$race_new <- "Unknown"
cohort_new[is.na(cohort_new$race_new),]
#ethnicity regroup
cohort_new <- add_column(cohort_new, ethnicity_new = NA)
cohort_new[cohort_new$ethnicity %in% c("Not of Spanish/Hispanic Origin",
                                       "Not of Spanish/Hispanic Origin, Unknown"),]$ethnicity_new <- "Not Hispanic"
cohort_new[cohort_new$ethnicity %in% c("Patient Refused","Unknown",
                                       "Unknown, Not of Spanish/Hispanic Origin",NA),]$ethnicity_new <- "Unknown"
cohort_new[is.na(cohort_new$ethnicity_new),]$ethnicity_new <- "Hispanic"
cohort_new[is.na(cohort_new$ethnicity_new),]
cohort_new[is.na(cohort_new$race_new),]$race
cohort_new[is.na(cohort_new$ethnicity_new),]$ethnicity
```

(9) group_give

average and the sd of the number

```{r}
length1 = rep(0,length(group_give_all))
for (i in seq_along(group_give_all)) {
  length1[i] = nrow(group_give_all[[i]])
}
mean(length1)
sd(length1)
```

for each simulation
```{r}
mean_groupa <- rep(0,length(group_give_all))
sd_groupa <- rep(0,length(group_give_all))
gender_percent_groupa <- 0
gender_number_groupa <- 0
race_percent_groupa <- NULL
race_number_groupa <- NULL
ethnicity_percent_groupa <- NULL
ethnicity_number_groupa <- NULL
outcome_percent_groupa <- NULL
outcome_number_groupa <- NULL
for (j in seq_along(group_give_all)) {
  #cat("i = ", j, "\n")
groupa <- group_give_all[[j]]$pat_enc_csn_id
groupa_id <- group_give_all[[j]]$pat_id
#AGE
age_groupa <- rep(0,length(groupa))
for (i in 1:length(groupa)) {
age_groupa[i] <- max(cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$"age")
}
mean_groupa[j] <- mean(age_groupa,na.rm = T)
sd_groupa[j] <- sd(age_groupa,na.rm = T) 
#GENDER
gender_groupa <- rep(0,length(groupa))
for (i in 1:length(groupa)) {
 gender_groupa[i] <- unique(cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$sex)
}
t1 <- table(gender_groupa)
gender_percent_groupa <- t1/length(groupa) + gender_percent_groupa
gender_number_groupa <- t1 + gender_number_groupa
#RACE
race_groupa <- rep(0,length(groupa))
for (i in 1:length(groupa)) {
 race_groupa[i] <- unique(cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$race_new)
}
t2 <- table(race_groupa)
race_percent_groupa[[j]] <- t2/length(groupa)
race_number_groupa[[j]] <- t2
#ETHNICITY
eth_groupa <- rep(0,length(groupa))
for (i in 1:length(groupa)) {
 eth_groupa[i] <- unique(cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$ethnicity_new)
}
t3 <- table(eth_groupa)
ethnicity_percent_groupa[[j]] <- t3/length(groupa)
ethnicity_number_groupa[[j]] <- t3
#OUTCOME
middle <- NULL
outcome_groupa <- as.character(rep(0,length(groupa_id)))
for (i in seq_along(groupa)) {
  middle[[i]] <- cohort_new[cohort_new$pat_id %in% groupa_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$"dead"
  if(sum(middle[[i]] %in% "deceased") > 0){
    outcome_groupa[i] <- "deceased" 
  } else {
    outcome_groupa[i] <- "alive" 
  }
}
t4 <- table(outcome_groupa)
outcome_percent_groupa[[j]] <- t4/length(groupa_id)
outcome_number_groupa[[j]] <- t4
}

```

sofa score
```{r}
score_bl <- NULL
for (i in seq_along(group_give_all)) {
  score_bl[[i]] <- as.numeric(as.character(group_give_all[[i]]$maryland_adjusted))
}
summary(sapply(score_bl, mean))
#the sd
sd(sapply(score_bl, mean))
```

the day - group a
```{r}
day_bl <- NULL
for (i in seq_along(group_give_all)) {
  day_bl[[i]] <- group_give_all[[i]]$intubated_day
}
summary(sapply(day_bl, mean))
```

age
```{r}
mean(mean_groupa) #mean
mean(sd_groupa) #sd
```


gender
```{r}
gender_number_groupa/length(group_give_all)
gender_percent_groupa/length(group_give_all)
```

race
```{r}
race_percent <- rep(0,5)
race_number <- rep(0,5)
names(race_percent) <- names(race_number) <- c("African American","Asian","Unknown","White","Native American")
for (j in seq_along(race_percent_groupa)) {
race_percent["African American"] <- race_percent["African American"] + race_percent_groupa[[j]]["African American"]
race_percent["Asian"] <- race_percent["Asian"] + race_percent_groupa[[j]]["Asian"]
race_percent["Unknown"] <- race_percent["Unknown"] + race_percent_groupa[[j]]["Unknown"]
race_percent["White"] <- race_percent["White"] + race_percent_groupa[[j]]["White"]
if(!is.na(race_percent_groupa[[j]]["Native American"])){
race_percent["Native American"] <- race_percent["Native American"] + race_percent_groupa[[j]]["Native American"]
}
race_number["African American"] <- race_number["African American"] + race_number_groupa[[j]]["African American"]
race_number["Asian"] <- race_number["Asian"] + race_number_groupa[[j]]["Asian"]
race_number["Unknown"] <- race_number["Unknown"] + race_number_groupa[[j]]["Unknown"]
race_number["White"] <- race_number["White"] + race_number_groupa[[j]]["White"]
if(!is.na(race_number_groupa[[j]]["Native American"])){
race_number["Native American"] <- race_number["Native American"] + race_number_groupa[[j]]["Native American"]
}
}
race_number/length(group_give_all)
race_percent/length(group_give_all)
```

ethnicity
```{r}
ethnicity_percent <- rep(0,3)
ethnicity_number <- rep(0,3)
names(ethnicity_percent) <- names(ethnicity_number) <- c("Hispanic","Not Hispanic","Unknown")
for (j in seq_along(ethnicity_percent_groupa)) {
ethnicity_percent["Hispanic"] <- ethnicity_percent["Hispanic"] + ethnicity_percent_groupa[[j]]["Hispanic"]
ethnicity_percent["Not Hispanic"] <- ethnicity_percent["Not Hispanic"] + ethnicity_percent_groupa[[j]]["Not Hispanic"]
if(!is.na(ethnicity_percent_groupa[[j]]["Unknown"])){
ethnicity_percent["Unknown"] <- ethnicity_percent["Unknown"] + ethnicity_percent_groupa[[j]]["Unknown"]
}

ethnicity_number["Hispanic"] <- ethnicity_number["Hispanic"] + ethnicity_number_groupa[[j]]["Hispanic"]
ethnicity_number["Not Hispanic"] <- ethnicity_number["Not Hispanic"] + ethnicity_number_groupa[[j]]["Not Hispanic"]
if(!is.na(ethnicity_number_groupa[[j]]["Unknown"])){
ethnicity_number["Unknown"] <- ethnicity_number["Unknown"] + ethnicity_number_groupa[[j]]["Unknown"]
}
}
ethnicity_number/length(group_give_all)
ethnicity_percent/length(group_give_all)
```

outcome
```{r}
outcome_percent <- rep(0,2)
outcome_number <- rep(0,2)
names(outcome_percent) <- names(outcome_number) <- c("alive","deceased")
for (j in seq_along(ethnicity_percent_groupa)) {
outcome_percent["alive"] <- outcome_percent["alive"] + outcome_percent_groupa[[j]]["alive"]
outcome_percent["deceased"] <- outcome_percent["deceased"] + outcome_percent_groupa[[j]]["deceased"]

outcome_number["alive"] <- outcome_number["alive"] + outcome_number_groupa[[j]]["alive"]
outcome_number["deceased"] <- outcome_number["deceased"] + outcome_number_groupa[[j]]["deceased"]
}
outcome_percent/length(group_give_all)
#sd of the percentage of the outcome
sd1 = rep(0,length(ethnicity_percent_groupa))
for (j in seq_along(ethnicity_percent_groupa)) {
sd1[j] =  outcome_percent_groupa[[j]]["alive"]
}
sd(sd1)
outcome_number/length(group_give_all)
#sd of the number of the outcome
sd2 = rep(0,length(ethnicity_percent_groupa))
for (j in seq_along(ethnicity_percent_groupa)) {
sd2[j] =  outcome_number_groupa[[j]]["alive"]
}
sd(sd2)
```

(10) group_receive

average and the sd of the number

```{r}
length2 = rep(0,length(group_receive_all))
for (i in seq_along(group_receive_all)) {
  length2[i] = nrow(group_receive_all[[i]])
}
mean(length2)
sd(length2)
```

for each simulation
```{r}
mean_groupb <- rep(0,length(group_receive_all))
sd_groupb <- rep(0,length(group_receive_all))
gender_percent_groupb <- 0
gender_number_groupb <- 0
race_percent_groupb <- NULL
race_number_groupb <- NULL
ethnicity_percent_groupb <- NULL
ethnicity_number_groupb <- NULL
outcome_percent_groupb <- NULL
outcome_number_groupb <- NULL
for (j in seq_along(group_receive_all)) {
  #cat("i = ", j, "\n")
groupb_15 <- group_receive_all[[j]]$pat_enc_csn_id
groupb_15_id <- group_receive_all[[j]]$pat_id
#AGE
age_groupb <- rep(0,length(groupb_15))
for (i in 1:length(groupb_15)) {
age_groupb[i] <- max(cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$"age")
}
mean_groupb[j] <- mean(age_groupb,na.rm = T)
sd_groupb[j] <- sd(age_groupb,na.rm = T) 
#GENDER
gender_groupb <- rep(0,length(groupb_15))
for (i in 1:length(groupb_15)) {
 gender_groupb[i] <- unique(cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$sex)
}
t1 <- table(gender_groupb)
gender_percent_groupb <- t1/length(groupb_15) + gender_percent_groupb
gender_number_groupb <- t1 + gender_number_groupb
#RACE
race_groupb <- rep(0,length(groupb_15))
for (i in 1:length(groupb_15)) {
 race_groupb[i] <- unique(cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$race_new)
}
t2 <- table(race_groupb)
race_percent_groupb[[j]] <- t2/length(groupb_15)
race_number_groupb[[j]] <- t2
#ETHNICITY
eth_groupb <- rep(0,length(groupb_15))
for (i in 1:length(groupb_15)) {
 eth_groupb[i] <- unique(cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$ethnicity_new)
}
t3 <- table(eth_groupb)
ethnicity_percent_groupb[[j]] <- t3/length(groupb_15)
ethnicity_number_groupb[[j]] <- t3
#OUTCOME
middle <- NULL
outcome_groupb <- as.character(rep(0,length(groupb_15_id)))
for (i in seq_along(groupb_15)) {
  middle[[i]] <- cohort_new[cohort_new$pat_id %in% groupb_15_id[i] & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]$"dead"
  if(sum(middle[[i]] %in% "deceased") > 0){
    outcome_groupb[i] <- "deceased" 
  } else {
    outcome_groupb[i] <- "alive" 
  }
}
t4 <- table(outcome_groupb)
outcome_percent_groupb[[j]] <- t4/length(groupb_15_id)
outcome_number_groupb[[j]] <- t4
}
```

score
```{r}
score_bl <- NULL
for (i in seq_along(group_receive_all)) {
  score_bl[[i]] <- as.numeric(as.character(group_receive_all[[i]]$maryland_adjusted))
}
summary(sapply(score_bl, mean))
#the sd
sd(sapply(score_bl, mean))
```

age
```{r}
mean(mean_groupb) #mean
mean(sd_groupb) #sd
```

gender
```{r}
gender_number_groupb/length(group_receive_all)
gender_percent_groupb/length(group_receive_all)
```

race
```{r}
race_percent <- rep(0,5)
race_number <- rep(0,5)
names(race_percent) <- names(race_number) <- c("African American","Asian","Unknown","White","Native American")
for (j in seq_along(race_percent_groupb)) {
race_percent["African American"] <- race_percent["African American"] + race_percent_groupb[[j]]["African American"]
race_percent["Asian"] <- race_percent["Asian"] + race_percent_groupb[[j]]["Asian"]
race_percent["Unknown"] <- race_percent["Unknown"] + race_percent_groupb[[j]]["Unknown"]
race_percent["White"] <- race_percent["White"] + race_percent_groupb[[j]]["White"]
if(!is.na(race_percent_groupb[[j]]["Native American"])){
race_percent["Native American"] <- race_percent["Native American"] + race_percent_groupb[[j]]["Native American"]
}
race_number["African American"] <- race_number["African American"] + race_number_groupb[[j]]["African American"]
race_number["Asian"] <- race_number["Asian"] + race_number_groupb[[j]]["Asian"]
race_number["Unknown"] <- race_number["Unknown"] + race_number_groupb[[j]]["Unknown"]
race_number["White"] <- race_number["White"] + race_number_groupb[[j]]["White"]
if(!is.na(race_number_groupb[[j]]["Native American"])){
race_number["Native American"] <- race_number["Native American"] + race_number_groupb[[j]]["Native American"]
}
}
race_number/length(group_receive_all)
race_percent/length(group_receive_all)
```


ethnicity
```{r}
ethnicity_percent <- rep(0,3)
ethnicity_number <- rep(0,3)
names(ethnicity_percent) <- names(ethnicity_number) <- c("Hispanic","Not Hispanic","Unknown")
for (j in seq_along(ethnicity_percent_groupb)) {
ethnicity_percent["Hispanic"] <- ethnicity_percent["Hispanic"] + ethnicity_percent_groupb[[j]]["Hispanic"]
ethnicity_percent["Not Hispanic"] <- ethnicity_percent["Not Hispanic"] + ethnicity_percent_groupb[[j]]["Not Hispanic"]
if(!is.na(ethnicity_percent_groupb[[j]]["Unknown"])){
ethnicity_percent["Unknown"] <- ethnicity_percent["Unknown"] + ethnicity_percent_groupb[[j]]["Unknown"]
}

ethnicity_number["Hispanic"] <- ethnicity_number["Hispanic"] + ethnicity_number_groupb[[j]]["Hispanic"]
ethnicity_number["Not Hispanic"] <- ethnicity_number["Not Hispanic"] + ethnicity_number_groupb[[j]]["Not Hispanic"]
if(!is.na(ethnicity_number_groupb[[j]]["Unknown"])){
ethnicity_number["Unknown"] <- ethnicity_number["Unknown"] + ethnicity_number_groupb[[j]]["Unknown"]
}

}
ethnicity_number/length(group_receive_all)
ethnicity_percent/length(group_receive_all)
```

outcome
```{r}
outcome_percent <- rep(0,2)
outcome_number <- rep(0,2)
names(outcome_percent) <- names(outcome_number) <- c("alive","deceased")
for (j in seq_along(ethnicity_percent_groupb)) {
outcome_percent["alive"] <- outcome_percent["alive"] + outcome_percent_groupb[[j]]["alive"]
outcome_percent["deceased"] <- outcome_percent["deceased"] + outcome_percent_groupb[[j]]["deceased"]

outcome_number["alive"] <- outcome_number["alive"] + outcome_number_groupb[[j]]["alive"]
outcome_number["deceased"] <- outcome_number["deceased"] + outcome_number_groupb[[j]]["deceased"]
}
outcome_percent/length(group_receive_all)
#sd of the percentage of the outcome
sd1 = rep(0,length(ethnicity_percent_groupa))
for (j in seq_along(ethnicity_percent_groupa)) {
sd1[j] =  outcome_percent_groupb[[j]]["alive"]
}
sd(sd1)
outcome_number/length(group_receive_all)
#sd of the number of the outcome
sd2 = rep(0,length(ethnicity_percent_groupa))
for (j in seq_along(ethnicity_percent_groupa)) {
sd2[j] =  outcome_number_groupb[[j]]["alive"]
}
sd(sd2)
```

(11) Severe comorbidity

```{r}
a <- table(cohort_new$pat_id) > 1
more2 <- names(table(cohort_new$pat_id))[a]
se_cor <- cohort_new[cohort_new$severe_comor == 1 & cohort_new$intubation_date < "2020-04-15" & cohort_new$extubation_date > "2020-03-30",]
se_cor <- se_cor[!is.na(se_cor$pat_enc_csn_id),]
#enroll for once
group_all1 <- se_cor$pat_id[!se_cor$pat_id %in% more2] 
#enroll for several times
group_all2 <- se_cor$pat_id[se_cor$pat_id %in% more2]  #0 patient
```

Age
```{r}
#age
#enroll for once
age_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$"age" 
format(x = mean(age_all, na.rm = T),digits = 6)
format(sd(age_all, na.rm = T),digits = 6)
```

Gender
```{r}
#gender
#enroll for once
gender_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$sex
t1 <- table(gender_all)
t1
t1/length(gender_all)
```

Race
```{r}
#race
#enroll for once
race_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$race_new
t2 <- table(race_all)
t2
t2/length(race_all)
```

Ethnicity
```{r}
#Ethnicity
#enroll for once
eth_all <- cohort_new[cohort_new$pat_id %in% group_all1,]$ethnicity_new
t3 <- table(eth_all)
t3
t3/length(eth_all)
```

whether they live in the real world (Pre-allocation)
```{r}
#cohort_new[is.na(cohort_new$dead),]$dead <- 0
#cohort_new$dead <- as.character(cohort_new$dead)
#cohort_new[cohort_new$dead == "1",]$dead <- "deceased"
#cohort_new[cohort_new$dead == "0",]$dead <- "alive"
#outcome
outcome_all <- as.character(rep(0,length(group_all1)))
for (i in seq_along(group_all1)) {
  outcome_all[i] <- cohort_new[cohort_new$pat_id == group_all1[i],]$"dead" 
}
t4 <- table(outcome_all)
t4
t4/length(outcome_all)
```


whether they live in the real world (Post-allocation)
```{r}
post_rate <- rep(0,100)
post_n <- rep(0,100)
for (i in 1:100) {
  #cat("seed = ", i, "\n")
  outcome_all <- rep("deceased",length(group_all1))
  adf_id <- unique(sofa3_all[[i]]$pat_id)
  id_live <- group_all1[group_all1 %in% adf_id] 
#outcome
  if(length(id_live) == 0){
    outcome_all <- outcome_all
  } else {
    outcome_all[1:length(id_live)] <- cohort_new[cohort_new$pat_id %in% id_live,]$"dead"
  }
  post_rate[i] <- table(outcome_all)["alive"]/length(outcome_all)
  post_n[i] <- as.numeric(table(outcome_all)["alive"])
}

post_rate[is.na(post_rate)] <- 0
mean(post_rate)
sd(post_rate)
```

how many patients were part of group_give

```{r}
n_give <- NULL
for (i in 1:100) {
  group_all <- c(group_all1,group_all2)
  g_id <- group_give_all[[i]]$pat_id
  n_give <- c(n_give,sum(group_all %in% g_id))
}
mean(n_give)
sd(n_give)
```








